Model 1: COVID model without Antibody response 
Creating separate function: Cov, vectors: parameters, state and init function pint()

```{r}
library(readr)
library(deSolve)

# Set the start and end time for the model simulation
day_start <- 0
day_stop <- 100
times <- seq(day_start, day_stop, by = 1/24)

pint<-function()
  {
#MODEL PARAMETERS INITIALISE
parameters <- c(p=3.07, #Viral production rate
                ki=3.5*10^-8,  #Rate of infection of Target cells per infected cell
                di=0.8,#Death rate of infected cells
                dv=2.3,#Clearance rate of viral particles
                g=0,#Growth rate of epithelial cells taken 0 in this simualtion
                K=4*10^8)
parameters}  

parameters<-pint()
initV<-1#Initial viral load from Vargas et al.
initI<-0 # Initial infected cells
initE<-4*10^8 # Target cells (Epithelial cells in the URT) From Baccam et al. 
state <- c(V=initV, I=initI, E=initE) 


# set up a function to solve the equations
Cov<-function(t, state, parameters) 
{
  with(as.list(c(state, parameters)),
       {
         # rate of change
         dV<- p*I-dv*V
         dI<- ki*V*E-di*I
         dE<- -ki*V*E +g*E*(1-((E+I)/K))

         # return the rate of change
         list(c(dV,dI,dE))
       }
  ) 
}
# run the model
out <- ode(y = state, times = times, func = Cov, parms = parameters)

#Store the basic output in vectors
model1<-out
    fv<-model1[,'V']
    lfv<-log10(fv)
    ic<-model1[,'I']
    tc<-model1[,'E']
    time<-model1[,'time']
    
```

Model 2:    COVID target cell model with immune response
Adding B cells and Antibody production: IgG and IgM separately.
Creating separate function: Cov_i, vectors: parameters_i, state_i and init function pint_i

```{r}
library(readr)
library(deSolve)

# Set the start and end time for the model simulation
day_start <- 0
day_stop <- 180
times <- seq(day_start, day_stop, by = 1/24)

#MODEL PARAMETERS INITIALISE
pint_i<-function(){
parameters <- c(p=2.5, #Viral production rate (Fitting)
                ki=3.5*10^-8,  #Rate of infection of Target cells per infected cell (Fitting)
                di=1.07,#Death rate of infected cells (Kim et al, Fitting)
                dv=2.3, #Clearance of viral particles (Fitting)
                um=0.005,#Rate of viral neutralization by IgM
                am=0.0,#Rate of IgM consumption because of neutralization
                ug=0.05,#Rate of viral neutralization by IgG
                ag=0.0,#Rate of IgG consumption because of neutralization
                b1=10^-4,# Rate of B cell activation because of virus
                b2=0.05,#B cell deactivation
                pm=100, #IgM production rate
                pg=80,#IgG production rate
                rm=0.25,#IgM degradation rate
                rg=0.01,
                g=0.8,
                K=4*10^8) #IgG degradation rate
}
parameters_i<-pint_i()
                       
initV<-0.31#Initial viral laod
initI<-0 # Intial infected cells
initE<-4*10^8 # Target cells (Epithelial cells in the URT)


state_i <- c(V=initV, I=initI, E=initE, B=0, Am=0, Ag=0)
# set up a function to solve the equations
Cov_i<-function(t, state_i, parameters) 
{
  with(as.list(c(state_i, parameters)),
       {
         # define variables
         

         
         # rate of change
         dE<- -ki*V*E +g*E*(1-((E+I)/K))
         dI<- ki*V*E-di*I
         dV<- p*I-dv*V -um*V*Am -ug*V*Ag
         dB<-b1*V*(1-B)-b2*B
         dAm<-pm*B-rm*Am-am*V*Am
         dAg<-pg*B-rg*Ag-ag*V*Ag
         # return the rate of change
         list(c(dV,dI,dE,dB,dAm,dAg))
       }
  ) 
  
}
# run the model
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)

# a simple plot of the model output
plot(out)

model1_i<-out
    fv_i<-model1[,'V']
    lfv_i<-log10(fv)
    ic_i<-model1[,'I']
    tc_i<-model1[,'E']

```

Plotting basic target cell model output:
Option of adding regeneration term g=0.8

```{r}

library(ggplot2)
library(ggpubr)
library(ggthemes)
library(viridis)
library(RColorBrewer)
library(extrafont)
library(ggplot2)
loadfonts(device = "win")
windowsFonts(Times = windowsFont("Century"))
library(scales) # to access break formatting functions
#font_import()


theme_set(theme(title=element_text(family='Garamond',size=16), plot.title = element_text(hjust = 0.5,face="bold",size=18),
          strip.background = element_rect(fill="#F2D6CE",color="#FFFFFF"),
          axis.text = element_text(family="Garamond",size=14),
          strip.text = element_text(family="Garamond",size=14,face="bold"),
          strip.placement = "outside",
          legend.key.size = unit(2,"line"),
          legend.text = element_text(family="Garamond",size=14)))

#Figure 4: 
f1<-ggplot()+ 
          geom_line(aes(x=time,y=fv,color='Free virus'),size=0.8)+ ylab('Viral RNA copies/ml, Count')+xlab('Time in days')+
          ggtitle("SARS-CoV2 infection dynamics") +labs(color = 'Compartment')+xlim(0,20)+ 
          geom_line(aes(x=time,y=tc,color='Target cells'),size=0.6)+xlab('Time in days')+
          geom_line(aes(x=time,y=ic,color='Infected cells'),size=0.8)+
          theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.text = element_text(family="Century",size=15))
          

ggsave("Basic_Model.tiff", plot = last_plot(),path ="C:/Users/Rutuja Chhajed/OneDrive - Nexus365/FIND/Model/Outputs/v2plots",units="in", width=10, height=4, dpi=300, compression = "lzw")



#Figure 5
f2<- ggplot()+
        geom_line(aes(x=time,y=lfv,color='Free virus'),size=0.8)+labs(color = 'Compartment') + ylab('log 10 RNA copies/ml')+
        xlab('Time in days')+
        xlim(0,30)+
        geom_line(aes(x=time,y=log10(tc),color='Target cells'),size=0.8)+
        ylim(-2,9)+ ylab('Log10 [Viral RNA copies/ml, Count]')+xlab('Time in days')+
        labs(color = 'Compartment')+ggtitle("SARS-CoV2 infection dynamics (Log10 scale)")+
        theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.text = element_text(family="Century",size=15))

ggsave("Basic_Model.tiff", plot = f1,path ="C:/Users/Rutuja Chhajed/OneDrive - Nexus365/FIND/Model/Outputs/v2plots",units="in", width=10, height=4, dpi=300, compression = "lzw")

#Figure 6
f1_norm<-ggplot()+ 
          geom_line(aes(x=time,y=fv/max(fv),color='Free virus'),size=0.8)+ ylab('Percentage')+xlab('Time in days')+
          ggtitle("SARS-CoV2 infection dynamics") +labs(color = 'Compartment')+xlim(0,20)+ 
          geom_line(aes(x=time,y=tc/max(tc),color='Target cells'),size=0.6)+xlab('Time in days')+
          geom_line(aes(x=time,y=ic/max(ic),color='Infected cells'),size=0.8)+
          theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.text = element_text(family="Century",size=15))


    
```

#Figure 7
Model2: Output for Base model with regeneration of target cells
```{r}
parameters<-pint()
parameters['g']<-0.8
model2 <- ode(y = state, times = times, func = Cov, parms = parameters)
model2<-as.data.frame(model2)


    p7<- ggplot()+ 
        geom_line(aes(x=time,y=log10(model2$V),color="Free virus"),size=0.8)+ 
        geom_line(aes(x=time,y=log10(model2$E),color='Target cells'),size=0.4,linetype='dashed')+ 
        ylab('Free virus:log 10 copies/ml')+   xlab('Time in days')+ylim(-2,10)+
        labs(color = 'Model') +ggtitle('Viral dynamics with Epithelial regeneration')+
        theme_minimal()+
        theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.text = element_text(family="Century",size=15))

```




Comparing response with and without humoral immunity without regeneration
Model 1= COntains output from Base model with g=0
Model 1_i= COntains output from Full model with g=0

Figure 8: SARS-CoV2 infection dynamics from base model and full model without epithelial regeneration.
```{r}

#Figure 8: BAse vs Full model without regenrration

library(ggplot2)
library(ggpubr)
library(ggthemes)
library(viridis)
library(RColorBrewer)
library(extrafont)
library(ggplot2)
loadfonts(device = "win")
windowsFonts(Times = windowsFont("Garamond"))
library(scales) # to access break formatting functions
#font_import()
times <- seq(day_start, 150, by = 1/24)

parameters <- pint()
out <- ode(y = state, times = times, func = Cov, parms = parameters)
model1<-as.data.frame(out)


state_i <- c(V=initV, I=initI, E=initE, B=0, Am=0, Ag=0)
parameters_i <- pint_i()
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)

model1_i<-as.data.frame(out)
    fv_i<-out[,'V']
    lfv_i<-log10(fv_i)
    ic_i<-out[,'I']
    abm<-out[,'Am']
    abg<-out[,'Ag']

library(ggplot2)
library(ggthemes) # Load
 
    
#Figure 8: SARS-CoV2 infection dynamics from base model and full model without epithelial regeneration.
p8<- ggplot()+ 
        geom_line(aes(x=times,y=log10(model1$V),color='Without humoral immunity'),size=0.8)+ 
        geom_line(aes(x=times,y=log10(model1_i$V),color='With humonal immunity'),size=0.8)+ 
        ylab('Free virus:log 10 copies/ml')+   xlab('Time in days')+ylim(-2,10)+
        labs(color = 'Model') +ggtitle('In-host SARS-Cov2 dynamics')+
        theme_pubr()+xlim(0,30)+
        theme_minimal()+
        theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))


#Difference in peak:
max(fv)/max(fv_i)
#27.82422
#Log scale=10^1.45

#Figure 9: SARS-CoV2 viral and antibody from the full model
#Final plot of all dynamics! Virus, IgM and IgG without regeneration

p9<-ggplot()+ 
   geom_line(aes(x=times,y=log10(model1_i$V),color='Viral load'),size=0.8)+ 
   geom_line(aes(x=times,y=model1_i$Am/100,color='IgM'),size=0.8) +
   geom_line(aes(x=times,y=model1_i$Ag/200,color='IgG'),size=0.8) +
   scale_y_continuous( name = "Free virus log 10 copies/ml",sec.axis = sec_axis( trans=~.*100, name="Antibody response (au)"), limits = c(-1, 12)) +
   ylab('Free virus:log 10 copies/ml')+   xlab('Time in days')+labs(color = 'Model') +
   ggtitle('In-host SARS-Cov2 dynamics')+ theme_minimal()+ theme(text = element_text(size=12))+xlim(0,150) +
          theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
                  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9"),aesthetics = "color")

p10<-ggplot()+ 
   geom_line(aes(x=times,y=log10(model1_i$V)/max(log10(model1_i$V)),color='Viral load'),size=0.8)+ 
   geom_line(aes(x=times,y=model1_i$Am/max(model1_i$Am),color='IgM'),size=0.8) +
   geom_line(aes(x=times,y=model1_i$Ag/max(model1_i$Ag),color='IgG'),size=0.8) +
   ylab('Percentage')+   xlab('Time in days')+labs(color = 'Model') +
  ylim(0,1)+
   ggtitle('In-host SARS-Cov2 viral and antibody dynamics: Normalised')+ theme_minimal()+ theme(text = element_text(size=12))+xlim(0,50) +
          theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
                  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9"),aesthetics = "color")

abm_n<-model1_i$Am/max(model1_i$Am)
abg_n<-model1_i$Ag/max(model1_i$Ag)
abm_n<-round(abm_n,1)
match(0.5,abm_n)
match(0.5,abm_n)/24

which(abm_n==0.5)/24

#5.25-6 days to reach 50%
#39-43 days to drop to 50%

which(abm_n==1)/24
#13 days to reach its peak value, stays till 25th day and declines


abg_n<-round(abg_n,1)
match(0.5,abg_n)
match(0.5,abg_n)/24



which(abg_n==0.5)/24
#15-18 days to reach 50%
#130-150 days to drop to 50%

which(abg_n==1)/24
#37 days to reach peak and declines after 66 days?
```
Comparing response with and without humoral immunity with g=0.8

Figure 11: SARS-CoV2 infection dynamics from base model and full model with epithelial regeneration.

Model 2: Base with regeneration
Model 2_i= Full with regenration
```{r}
parameters<-pint()
parameters['g']<-0.8
model2 <- ode(y = state, times = times, func = Cov, parms = parameters)
model2<-as.data.frame(model2)

parameters_i<-pint_i()
parameters_i['g']<-0.8
model2_i<- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
model2_i<-as.data.frame(model2_i)
library(ggplot2)
library(ggthemes) # Load
library(ggpubr) # Load
p11<- ggplot()+ 
        geom_line(aes(x=times,y=log10(model2$V),color='Without humoral immunity'),size=0.8)+ 
        geom_line(aes(x=times,y=log10(model2_i$V),color='With humonal immune response'),size=0.8)+ 
        ylab('Free virus:log 10 copies/ml')+   xlab('Time in days')+
        labs(color = 'Model') +ggtitle('In-host SARS-Cov2 dynamics')+
        xlim(0,100)+ylim(-4,10)+
         theme_minimal()+
         theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))

          

```
Exploratory analysis for Model 2, with regeneration term

E1: Changing V(0)
Figure 13 and 14
```{r}
parameter_i<-pint_i()
parameters_i['g']<-0.8

state_i['V']<-0.1
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv1<-out[,'V']
if1<-out[,'I']
ab1<-out[,'Am']
abg1<-out[,'Ag']


state_i['V']<-1
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv2<-out[,'V']
if2<-out[,'I']
ab2<-out[,'Am']
abg2<-out[,'Ag']

state_i['V']<-100
out <-  ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv3<-out[,'V']
if3<-out[,'I']
ab3<-out[,'Am']
abg3<-out[,'Ag']

state_i['V']<-1000
out <-  ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv4<-out[,'V']
if4<-out[,'I']
ab4<-out[,'Am']
abg4<-out[,'Ag']



state_i['V']<-10000
out <-  ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv5<-out[,'V']
if5<-out[,'I']
ab5<-out[,'Am']
abg5<-out[,'Ag']


library(ggplot2)

  
 p13<- ggplot()+ 
          geom_line(aes(x=times,y=fv1,color='0.1X'),size=0.8)+
          geom_line(aes(x=times,y=fv2,color='1X'),size=0.8)+
          geom_line(aes(x=times,y=fv3,color='100X'),size=0.8)+
          geom_line(aes(x=times,y=fv4,color='1000X'),size=0.8)+
          geom_line(aes(x=times,y=fv5,color='10000X'),size=0.8)+
         ylab('Free virus (copies/ml)')+xlab('Time in days')+xlim(c(0,30))+
          labs(color = 'Initial viral load') +
          ggtitle('Viral dynamics and initial viral load')+ 
           theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
                  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9"),aesthetics = "color")

 
 

 #Change in viral peak: from 1X to 10000X
(max(fv5)- max(fv2))/max(fv2)
 #9% increase!
which.max(fv2)-which.max(fv5)
#
 p14<- ggplot()+ 
          geom_line(aes(x=times,y=log10(fv1),color='0.1X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv2),color='1X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv3),color='100X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv4),color='1000X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv5),color='10000X'),size=0.8)+
         ylab('Free virus (copies/ml)')+xlab('Time in days')+xlim(c(0,30))+
          labs(color = 'Initial viral load') +ylim(-1,10)+
          ggtitle('Viral dynamics and initial viral load')+ 
           theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
                  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#56B4E0","#56B6E9"),aesthetics = "color")
 

  
  #Not in the main text
plot_temp1<-   ggplot()+ 
   #geom_line(aes(x=times,y=ab0,color='A'),size=0.4)+
          geom_line(aes(x=times,y=ab1,color='1X'),size=0.4)+
          geom_line(aes(x=times,y=ab2,color='100X'),size=0.4)+
          geom_line(aes(x=times,y=ab3,color='1000X'),size=0.4)+
            geom_line(aes(x=times,y=ab4,color='10000X'),size=0.4)+ylab('IgM units')+xlab('Time in days')+xlim(c(0,30))+labs(color = 'Initial viral load') +ggtitle('In-host SARS-Cov2 dynamics: IgM')+ theme_stata()+  theme(text = element_text(size=12)) +
  scale_color_manual(values = c("1X", "100X", "1000X","10000X"))+ scale_colour_hc()
 
 
   #Not in the main text
  
plot_temp2 <- ggplot()+ 
   #geom_line(aes(x=times,y=ab0,color='A'),size=0.4)+
          geom_line(aes(x=times,y=abg1,color='1X'),size=0.4)+
          geom_line(aes(x=times,y=abg2,color='100X'),size=0.4)+
          geom_line(aes(x=times,y=abg3,color='1000X'),size=0.4)+
            geom_line(aes(x=times,y=abg4,color='10000X'),size=0.4)+ylab('IgM units')+xlab('Time in days')+xlim(c(0,60))+labs(color = 'Initial viral load') +ggtitle('In-host SARS-Cov2 dynamics: IgG')+ theme_stata()+  theme(text = element_text(size=12)) +
  scale_color_manual(values = c("1X", "100X", "1000X","10000X"))+ scale_colour_hc()

```

E2: Changing di
Figure 15, 16: Changes in viral dynamics with infected cell clearance rate for full model
```{r}

parameters_i<-pint_i()
parameters_i['g']<-0.8
state_i <- c(V=initV, I=initI, E=initE, B=0, Am=0, Ag=0)
times <- seq(day_start, day_stop, by = 1/24)

parameters_i['di']<-0.2
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv1<-out[,'V']
if1<-out[,'I']

parameters_i['di']<-0.5
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv2<-out[,'V']
if2<-out[,'I']


parameters_i['di']<-0.7
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv3<-out[,'V']
if3<-out[,'I']

parameters_i['di']<-1.07
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv4<-out[,'V']
if4<-out[,'I']

parameters_i['di']<-2
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv5<-out[,'V']
if5<-out[,'I']

library(ggplot2)

p15<-ggplot()+ 
          geom_line(aes(x=times,y=fv1,color='0.2'),size=0.8)+
          geom_line(aes(x=times,y=fv2,color='0.5'),size=0.8)+
          geom_line(aes(x=times,y=fv3,color='0.7'),size=0.8)+
          geom_line(aes(x=times,y=fv4,color='1.07'),size=0.8)+
            geom_line(aes(x=times,y=fv5,color='2'),size=0.8)+
          ylab('Free virus (copies/ml)')+xlab('Time in days')+xlim(c(0,60))+
          labs(color = 'di: per day') +
          ggtitle('Viral dynamics and infected cell clearance rate (di)')+ 
            theme_minimal()+
         theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))



p16<-ggplot()+ 
          geom_line(aes(x=times,y=log10(fv1),color='0.2'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv2),color='0.5'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv3),color='0.7'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv4),color='1.07'),size=0.8)+
            geom_line(aes(x=times,y=log10(fv5),color='2'),size=0.8)+
          ylab('Free virus (Log copies/ml)')+xlab('Time in days')+xlim(c(0,60))+ylim(0,10)+
          labs(color = 'di:per day') +
             ggtitle('Viral dynamics and infected cell clearance rate (di): Log scale')+ 
            theme_minimal()+
         theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))

  #scale_color_manual(values = c("1X", "100X", "1000X","10000X"))+ scale_colour_hc()
 

 #Change in viral peak: from 1X to 10000X
(max(fv2)- max(fv4))/max(fv4)
 #164% increase!
which.max(fv4)-which.max(fv2)
#
 #Change in viral peak: from 1X to 10000X
(max(fv5)- max(fv4))/max(fv4)
 #-0.88139 dncrease!


```
Figure 17-18: Changes in viral dynamics with viral clearance rate for full model
E3: Changing dv
```{r}
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(viridis)
library(RColorBrewer)
library(extrafont)
library(ggplot2)
loadfonts(device = "win")
windowsFonts(Times = windowsFont("Century"))
parameters_i<-pint_i()
parameters_i['g']<-0.8
state_i <- c(V=initV, I=initI, E=initE, B=0, Am=0, Ag=0)
times <- seq(day_start, day_stop, by = 1/24)


parameters_i['dv']<-0.6
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv1<-out[,'V']
if1<-out[,'I']

parameters_i['dv']<-1.2
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv2<-out[,'V']
if2<-out[,'I']


parameters_i['dv']<-2.4
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv3<-out[,'V']
if3<-out[,'I']

parameters_i['dv']<-4.8
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv4<-out[,'V']

if4<-out[,'I']


parameters_i['dv']<-6
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv5<-out[,'V']
if5<-out[,'I']
library(ggplot2)


  
 p17<- ggplot()+ 
          geom_line(aes(x=times,y=fv5,color='6'),size=0.8)+
          geom_line(aes(x=times,y=fv4,color='4'),size=0.8)+
          geom_line(aes(x=times,y=fv3,color='2.4'),size=0.8)+
          geom_line(aes(x=times,y=fv2,color='1.2'),size=0.8)+
             geom_line(aes(x=times,y=fv1,color='0.6'),size=0.8)+
          ylab('Free virus (copies/ml)')+xlab('Time in days')+xlim(c(0,30))+
     labs(color = 'dv: per day') +
          ggtitle('Viral dynamics and viral clearance rate (dv)')+ 
             theme_minimal()+
         theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
   scale_color_manual(values = c("6","4.8","2.4","1.2","0.6"))
 
 
  p18<- ggplot()+ 
          geom_line(aes(x=times,y=log10(fv5),color='6'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv4),color='4'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv3),color='2.4'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv2),color='1.2'),size=0.8)+
             geom_line(aes(x=times,y=log10(fv1),color='0.6'),size=0.8)+
          ylab('Log Free virus (copies/ml)')+xlab('Time in days')+xlim(c(0,30))+ylim(-1,8)+
     labs(color = 'dv: per day') +
          ggtitle('Viral dynamics and viral clearance rate (dv)')+ 
             theme_minimal()+
         theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
   scale_color_manual(values = c("6","4.8","2.4","1.2","0.6"))
  

 

 #Change in viral peak: From 2.4 to 1.2
(max(fv1)- max(fv2))/max(fv2)
 #30% increase!

  
  (max(fv5)- max(fv2))/max(fv2)
 #92% decrease
  
  
```
Exploratory analysis for Model 2, with regeneration term

E3: Changing V(0)
Figure 13 and 14
```{r}
parameter_i<-pint_i()
parameters_i['g']<-0.8

state_i['V']<-0.1
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv1<-out[,'V']
if1<-out[,'I']
ab1<-out[,'Am']
abg1<-out[,'Ag']


state_i['V']<-1
out <- ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv2<-out[,'V']
if2<-out[,'I']
ab2<-out[,'Am']
abg2<-out[,'Ag']

state_i['V']<-100
out <-  ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv3<-out[,'V']
if3<-out[,'I']
ab3<-out[,'Am']
abg3<-out[,'Ag']

state_i['V']<-1000
out <-  ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv4<-out[,'V']
if4<-out[,'I']
ab4<-out[,'Am']
abg4<-out[,'Ag']



state_i['V']<-10000
out <-  ode(y = state_i, times = times, func = Cov_i, parms = parameters_i)
fv5<-out[,'V']
if5<-out[,'I']
ab5<-out[,'Am']
abg5<-out[,'Ag']


library(ggplot2)

  
 p13<- ggplot()+ 
          geom_line(aes(x=times,y=fv1,color='0.1X'),size=0.8)+
          geom_line(aes(x=times,y=fv2,color='1X'),size=0.8)+
          geom_line(aes(x=times,y=fv3,color='100X'),size=0.8)+
          geom_line(aes(x=times,y=fv4,color='1000X'),size=0.8)+
          geom_line(aes(x=times,y=fv5,color='10000X'),size=0.8)+
         ylab('Free virus (copies/ml)')+xlab('Time in days')+xlim(c(0,30))+
          labs(color = 'Initial viral load') +
          ggtitle('Viral dynamics and initial viral load')+ 
           theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
                  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9"),aesthetics = "color")

 
 

 #Change in viral peak: from 1X to 10000X
(max(fv5)- max(fv2))/max(fv2)
 #9% increase!
which.max(fv2)-which.max(fv5)
#
 p14<- ggplot()+ 
          geom_line(aes(x=times,y=log10(fv1),color='0.1X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv2),color='1X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv3),color='100X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv4),color='1000X'),size=0.8)+
          geom_line(aes(x=times,y=log10(fv5),color='10000X'),size=0.8)+
         ylab('Free virus (copies/ml)')+xlab('Time in days')+xlim(c(0,30))+
          labs(color = 'Initial viral load') +ylim(-1,10)+
          ggtitle('Viral dynamics and initial viral load')+ 
           theme_minimal()+
          theme(title=element_text(family='Century',size=16), plot.title = element_text(hjust = 0.5,vjust = 1, face="bold",size=18),
                  strip.background = element_rect(fill="#F2D6CE",color="#FFFFFE"),
                  axis.text = element_text(family="Century",size=15),
                  strip.text = element_text(family="Century",size=15,face="bold"),
                  strip.placement = "outside",legend.key.size = unit(1.5,"line"),
                  legend.position="bottom",
                  legend.text = element_text(family="Century",size=15))+
                  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#56B4E0","#56B6E9"),aesthetics = "color")
 

  
  #Not in the main text
plot_temp1<-   ggplot()+ 
   #geom_line(aes(x=times,y=ab0,color='A'),size=0.4)+
          geom_line(aes(x=times,y=ab1,color='1X'),size=0.4)+
          geom_line(aes(x=times,y=ab2,color='100X'),size=0.4)+
          geom_line(aes(x=times,y=ab3,color='1000X'),size=0.4)+
            geom_line(aes(x=times,y=ab4,color='10000X'),size=0.4)+ylab('IgM units')+xlab('Time in days')+xlim(c(0,30))+labs(color = 'Initial viral load') +ggtitle('In-host SARS-Cov2 dynamics: IgM')+ theme_stata()+  theme(text = element_text(size=12)) +
  scale_color_manual(values = c("1X", "100X", "1000X","10000X"))+ scale_colour_hc()
 
 
   #Not in the main text
  
plot_temp2 <- ggplot()+ 
   #geom_line(aes(x=times,y=ab0,color='A'),size=0.4)+
          geom_line(aes(x=times,y=abg1,color='1X'),size=0.4)+
          geom_line(aes(x=times,y=abg2,color='100X'),size=0.4)+
          geom_line(aes(x=times,y=abg3,color='1000X'),size=0.4)+
            geom_line(aes(x=times,y=abg4,color='10000X'),size=0.4)+ylab('IgM units')+xlab('Time in days')+xlim(c(0,60))+labs(color = 'Initial viral load') +ggtitle('In-host SARS-Cov2 dynamics: IgG')+ theme_stata()+  theme(text = element_text(size=12)) +
  scale_color_manual(values = c("1X", "100X", "1000X","10000X"))+ scale_colour_hc()

```
 